(Automatic) Speech Recognition Project --- Attacks on Neural Networks in a Lightweight Speech Pseudonymization Pipeline

### 2024-06-06 paper/paper.tex
Finished the paper

\begin{abstract}

\end{abstract}

@@

\section{Related Work}
\subsection{Neural Speaker Anonymization}
\citet{meyer2023anonymizing} showcase a successful realization of neural Speaker Anonymization using GANs.
Their Speaker Anonymization architecture includes the extraction of embeddings from speech, which are fed into a GAN.
This GAN first learns to generate embeddings sampled from a normal distribution.
After every sample, it then learns to calculate the distance between the embedding that it generated, and an embedding extracted from speech it has been fed.
This training procedure teaches the GAN to generate embeddings that are similar to the speech embeddings.
Once training has been finished, embeddings based on real speech embeddings are sampled from the GAN until an embedding is generated whose cosine distance from the corresponding real speech embeddings is sufficiently large.
If the cosine distance is sufficiently large, the GAN should have produced an embedding that represents the contents of the speech utterance without representing the characteristics of the speaker found in the utterance.
This embedding is fed to an existing speech synthesis model, which produces anonymized speech.

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.9\textwidth]{roddeman_etal_optimization.png}
  \caption{The optimization process of the lightweight pseudonymization pipeline by \citet{roddeman2024anonymization}.}
  \label{fig:roddeman_etal_optimization}
\end{figure*}

@@

\citet{goodfellow2015explaining} introduced FGSM, the \textit{Fast Gradient Sign Method}.
FGSM perturbs an input by exploiting a trained model's gradients.
When given the input $x$ and its label $y$, an FGSM attack calculates the gradient with respect to the input using the model's parameters $\theta$ and loss function $J_\theta(x, y)$.
The sign of this gradient is calculated and is added on top of the original input by a factor of $\epsilon$.
The FGSM attack can then be defined as such:
\begin{align*}
  x_t &= x + \epsilon \cdot \text{sign}(\nabla_x J_\theta(x, y))
\end{align*}
where $x_t$ is the perturbed input.
A visualization of this process can be found in figure \ref{fig:fgsm}.

@@

@@

\subsubsection{Backdoor Attacks}
\begin{figure*}[h]
  \centering
  \includegraphics[width=0.9\textwidth]{badnet.png}
  \caption{An example of a BadNet attack \citep{gu2019badnets}. On the left, an image of a stop sign with varying BadNet backdoors can be seen. On the right, a backdoored network can be seen interpreting a stop sign as a speed limit sign due to the physical backdoor on the sign itself.}
  \label{fig:badnet}
\end{figure*}

Backdoor attacks are adversarial attacks that are used during model training.
They are a subset of \textit{Poisoning Attacks}.
The aim of a poisoning attack is to alter (a subset of) the training data in order to teach the model certain behavior or to decrease the model's performance.
Backdoor attacks are a specific type of poisoning attack where the attacker teaches a model to respond to a certain property of the data.
If the model encounters that property in a data sample, it should behave according to the attacker's goals.
This property is called a \textit{trigger}.

@@

We use the evasion attacks to generate perturbed utterances with the speaker with ID 0 as the target.
This means that the perturbations caused by the attack should move any utterance closer to the space of utterances by the speaker with ID 0.
We feed these perturbed inputs into the ASV model, and measure its Speaker Identification Accuracy and Attack Success Rate.
We also measure the clean ASR model's WER on these perturbed inputs.

@@

\section{Discussion}
The results show that a simple JingleBack backdoor can successfully be inserted into \citeauthor{roddeman2024anonymization}'s ASV model using only 5 backdoored speech utterances, and that this number of backdoored utterances is sufficient in making the model misclassify 95\% of all utterances with the JingleBack trigger inserted.
The accuracy of the ASV model is not compromised as this backdoor is learned, with the ASV model being able to identify at least 80\% of all speakers correctly when given an utterance without the trigger, which is a higher accuracy than the clean ASV model.
This combination of a good accuracy and near-perfect Attack Success Rate should fulfill the wishes of an attacker, who aims to exploit model behavior using the trigger, and wants the model to learn this trigger as effectively as possible, without decreasing the clean accuracy, which would raise suspicion.

@@

\section{Conclusion}
In this paper, we demonstrate how we can attack neural Speech Anonymization pipelines using adversarial attacks.
We demonstrate that a pipeline that optimizes for lightweight effects-based speaker pseudonymization using neural speech models can be backdoored using a JingleBack attack, where the trigger is also another audio effect, and that such an attack can introduce a near-perfect backdoor into the neural models with as little as five adversarial examples.
% Zeg ook nog een zin over evasion attacks.

>>>>

\begin{abstract}
  We explore potential weak points of a Speaker Anonymization system that uses a lightweight, digital effects-based pseudonymization strategy by adversarially attacking the neural speech models in the system used for evaluating the pseudonymization strategy.
  We successfully insert a JingleBack backdoor into the system's Automatic Speaker Verification model, reaching an Attack Success Rate of 95\% after providing only 5 backdoored utterances.
  We also show that the models are sensitive to FGSM and PGD attacks, and that small audio perturbations can lead to a remarkable decrease in model performance.
\end{abstract}

@@

\section{Related Work}
\subsection{Neural Speaker Anonymization}
\begin{figure*}
  \centering
  \includegraphics[width=0.9\textwidth]{roddeman_etal_optimization.png}
  \caption{The optimization process of the lightweight pseudonymization pipeline by \citet{roddeman2024anonymization}.}
  \label{fig:roddeman_etal_optimization}
\end{figure*}

\citet{meyer2023anonymizing} showcase a successful realization of neural Speaker Anonymization using GANs.
Their Speaker Anonymization architecture includes the extraction of embeddings from speech, which are fed into a GAN.
This GAN first learns to generate embeddings sampled from a normal distribution.
After every sample, it then learns to calculate the distance between the embedding that it generated, and an embedding extracted from speech it has been fed.
This training procedure teaches the GAN to generate embeddings that are similar to the speech embeddings.
Once training has been finished, embeddings based on real speech embeddings are sampled from the GAN until an embedding is generated whose cosine distance from the corresponding real speech embeddings is sufficiently large.
If the cosine distance is sufficiently large, the GAN should have produced an embedding that represents the contents of the speech utterance without representing the characteristics of the speaker found in the utterance.
This embedding is fed to an existing speech synthesis model, which produces anonymized speech.

@@

@@

\citet{goodfellow2015explaining} introduce FGSM, the \textit{Fast Gradient Sign Method}.
FGSM perturbs an input by exploiting a trained model's gradients.
When given the input $x$ and its label $y$, an FGSM attack calculates the gradient with respect to the input using the model's parameters $\theta$ and loss function $J_\theta(x, y)$.
The sign of this gradient is calculated and is added on top of the original input by a factor of $\epsilon$.
The FGSM attack can then be defined as such:
\begin{align*}
  x_t &= x + \epsilon \cdot \text{sign}(\nabla_x J_\theta(x, y))
\end{align*}
where $x_t$ is the perturbed input.
A visualization of this process can be found in figure \ref{fig:fgsm}.

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.9\textwidth]{badnet.png}
  \caption{An example of a BadNet attack \citep{gu2019badnets}. On the left, an image of a stop sign with varying BadNet backdoors can be seen. On the right, a backdoored network can be seen interpreting a stop sign as a speed limit sign due to the physical backdoor on the sign itself.}
  \label{fig:badnet}
\end{figure*}

@@

\subsubsection{Backdoor Attacks}
Backdoor attacks are adversarial attacks that are used during model training.
They are a subset of \textit{Poisoning Attacks}.
The aim of a poisoning attack is to alter (a subset of) the training data in order to teach the model certain behavior or to decrease the model's performance.
Backdoor attacks are a specific type of poisoning attack where the attacker teaches a model to respond to a certain property of the data.
If the model encounters that property in a data sample, it should behave according to the attacker's goals.
This property is called a \textit{trigger}.

@@

We use the evasion attacks to generate perturbed utterances with the speaker with ID 0 as the target.
This means that the perturbations caused by the attack should move any utterance closer to the space of utterances by the speaker with ID 0.
We feed these perturbed inputs into the ASV model, and measure its Speaker Identification Accuracy.
We also measure the clean ASR model's WER on these perturbed inputs.

@@

\subsection{Evasion Attacks}
\begin{table}[h]
    \centering
    \begin{tabular}{c|c|c}
        & \textbf{Acc} & \textbf{WER} \\
        \hline
        \textbf{Clean} & 0.62 & 0.104 \\
        \textbf{FGSM} & 0.10 & 0.773 \\
        \textbf{PGD} & 0.10 & 0.763
    \end{tabular}
    \caption{Scores of the Speaker Identification Accuracy (Acc) and Word Error Rate (WER) of the clean ASV and ASR models on unaltered/clean utterances, FGSM-perturbed utterances, and PGD-perturbed utterances from the test set.}
    \label{tab:evasion_metrics}
\end{table}

The results of the FGSM and PGD attack experiments are shown in table \ref{tab:evasion_metrics}.
After the utterances from the clean test set have been perturbed by an FGSM or PGD attack, the Speaker Identification Accuracy of the ASV model drops to 10\%.
Since the ASV model predicts from a pool of ten speakers, its accuracy is now no better than random guesses.
The ASR model's Word Error Rate has increased from 0.104 to 0.773 on FGSM-perturbed audio and 0.763 on PGD-perturbed audio.

\section{Discussion}
The results from the Backdoor Attack experiment show that a simple JingleBack backdoor can successfully be inserted into \citeauthor{roddeman2024anonymization}'s ASV model using only 5 backdoored speech utterances, and that this number of backdoored utterances is sufficient in making the model misclassify 95\% of all utterances with the JingleBack trigger inserted.
The accuracy of the ASV model is not compromised as this backdoor is learned, with the ASV model being able to identify at least 80\% of all speakers correctly when given an utterance without the trigger, which is a higher accuracy than the clean ASV model.
This combination of a good accuracy and near-perfect Attack Success Rate should fulfill the wishes of an attacker, who aims to exploit model behavior using the trigger, and wants the model to learn this trigger as effectively as possible, without decreasing the clean accuracy, which would raise suspicion.

@@

The results from the Evasion Attacks experiment show that perturbing the utterances with an FGSM or PGD attack worsens the models' performances staggeringly: the FGSM attack causes the Word Error Rate to increase over sevenfold, and the Speaker Identification Accuracy is no better than purely random guesses.
Despite its multi-step approach, the PGD attack causes the models to reach similar measures.
It is likely that the perturbations, despite maximally deviating from the original utterances by a factor only of $\frac{8}{255}$, are too large for the models to handle.
The size of the perturbations would prevent the generation of perturbed utterances that are still understandable by the models, which prevents an attacker from making the ASV model misclassify to a specific target speaker.
However, the effects of the perturbations does show that the ASR and ASV models are quite sensitive to perturbed audio, which could be used to an attacker's advantage.

\section{Conclusion}
In this paper, we demonstrate how we can attack neural Speech Anonymization pipelines using adversarial attacks.
We demonstrate that a pipeline that optimizes for lightweight effects-based speaker pseudonymization using neural speech models can be backdoored using a JingleBack attack, where the trigger is also another audio effect, and that such an attack can introduce a near-perfect backdoor into the neural models with as little as five adversarial examples.
Furthermore, we demonstrate that the neural speech models are sensitive to FGSM-perturbed and PGD-perturbed audio, and that their performance drops remarkably once given utterances affected by an Evasion Attack.
We conclude that adversarial attacks on Speaker Anonymization systems have the potential to disrupt the anonymization strategy and may prevent proper anonymization from being applied on spoken utterances.
